---
title: "OTS -> OCC"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r init}
rm(list=ls())
library(data.table)
library(lfe)
library(stargazer)
library(plyr)
library(reshape2)
library(lubridate)
library(ggplot2)
library(reshape2)
library(dplyr)




#variables
output.type="text"


# functions
printtable <- function(reg,column.labels,depvar,note,iv,lines) {
  stargazer(reg,type=output.type,no.space = TRUE,omit.stat = c("f","adj.rsq","ser"),notes= note,column.labels = column.labels, dep.var.labels = "",dep.var.caption   = paste("Y: ",gsub("_"," ",depvar),"; iv: ",gsub("_"," ",iv)),dep.var.labels.include = FALSE,add.lines = lines)
}

```

```{r}
hmda <- readRDS(file="C:/Users/dnratnadiwakara/Documents/interest rate and default/Data/Raw/HMDA/agency/agency_hmda.rds")
```


# Descriptives: Owneroccupied, new purchase
```{r}
stargazer(hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate>=2008, c("denied","amountofloan","loan_to_income","applicantincome","ots_lender","asofdate")], type = "text", summary.stat = c("mean","median","sd", "n"),notes = "",digits = 4)
```
# Descriptives: Owneroccupied, refinance
```{r}
stargazer(hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate>=2008, c("denied","amountofloan","loan_to_income","applicantincome","ots_lender","asofdate")], type = "text", summary.stat = c("mean","median","sd", "n"),notes = "",digits = 4)
```




# Propensity to deny: loan applications after 2008
```{r }

gc()
regs <- list()
regs[[1]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate>=2008])
gc()
regs[[2]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3"  & hmda$asofdate>=2008])

note =c("Fixed Effects:  MSA*Year, MSA*OTS, Race","Standard Errors clustered by MSA")


printtable(regs,c("New purchases","Refinances"),"denied",note,"none","")
rm(regs)
gc(verbose = FALSE)
```



# Propensity to deny: parellel trends
```{r }
hmda[,year:=as.factor(hmda$asofdate)]
hmda <- within(hmda, year <- relevel(year, ref = 8))
rm(regs)
gc()
regs <- list()
regs[[1]] <- felm(as.formula("denied~factor(year)*factor(ots_lender)+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate>=2008 ])
gc()
regs[[2]] <- felm(as.formula("denied~factor(year)*factor(ots_lender)+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate>=2008 ])

note =c("Fixed Effects:  MSA*Year, MSA*OTS, Race","Standard Errors clustered by MSA,Year")


printtable(regs,c("New purchases","Refinances"),"denied",note,"none","")
```

```{r}
coefs <- c(as.vector(regs[[1]]$coefficients[12:14]),0,as.vector(regs[[1]]$coefficients[15:17]))
se <- c(as.vector(regs[[1]]$cse[12:14]),0,as.vector(regs[[1]]$cse[15:17]))
se_lb <- coefs - se*1.96
se_ub <- coefs + se*1.96
years <- c(2008:2014)

df <- as.data.frame(cbind(years,coefs),stringsAsFactors = FALSE)

gr1<- ggplot(df, aes(x=years, y=coefs)) + geom_hline(yintercept = 0)+
  geom_point(color="red")+geom_errorbar(aes(ymin=se_lb, ymax=se_ub), width=0,position=position_dodge(0))+
  scale_x_continuous(breaks=years)+ theme_bw()+ylab(expression(beta[y])) + xlab("")+
  theme(legend.title=element_blank(),panel.border = element_blank(), axis.line.x = element_line(color = 'gray80'))
gr1

coefs <- c(as.vector(regs[[2]]$coefficients[12:14]),0,as.vector(regs[[2]]$coefficients[15:17]))
se <- c(as.vector(regs[[2]]$cse[12:14]),0,as.vector(regs[[2]]$cse[15:17]))
se_lb <- coefs - se*1.96
se_ub <- coefs + se*1.96
years <- c(2008:2014)

df <- as.data.frame(cbind(years,coefs),stringsAsFactors = FALSE)

gr2<- ggplot(df, aes(x=years, y=coefs)) + geom_hline(yintercept = 0)+
  geom_point(color="red")+geom_errorbar(aes(ymin=se_lb, ymax=se_ub), width=0,position=position_dodge(0))+
  scale_x_continuous(breaks=years)+ theme_bw()+ylab(expression(beta[y])) + xlab("")+
  theme(legend.title=element_blank(),panel.border = element_blank(), axis.line.x = element_line(color = 'gray80'))

gr2

```




# Fraction of OTS loans in census tracts in 2008-2009
```{r}
msa_summary_refin <- hmda[hmda$actiontaken %in% c(1,2,3) & hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate==2009, .(count = .N), by = list(censustract,ots_lender)]
msa_summary_refin <- dcast(msa_summary_refin,formula =censustract~ots_lender )
names(msa_summary_refin) <- c("censustract","nonots_refin","ots_refin")
# msa_summary_refin$nonots_refin <- ifelse(is.na(msa_summary_refin$nonots_refin),0,msa_summary_refin$nonots_refin)
# msa_summary_refin$ots_refin <- ifelse(is.na(msa_summary_refin$ots_refin),0,msa_summary_refin$ots_refin)
msa_summary_refin <- data.table(msa_summary_refin)
msa_summary_refin[,ots_pct_refin:=msa_summary_refin$ots_refin/(msa_summary_refin$ots_refin+msa_summary_refin$nonots_refin)]

msa_summary <- msa_summary_refin

msa_summary[,msa_loans_2009:=msa_summary$nonots_refin+msa_summary$ots_refin]
msa_summary[,c("nonots_purch","ots_purch","nonots_refin","ots_refin"):=list(NULL)]

# 
# hmda[,c("ots_pct_purch","ots_pct_refin","msa_loans_2009","ots_pct_purch_q","ots_pct_refin_q"):=list(NULL)]
# hmda<- merge(hmda,msa_summary,by="censustract",all.x = TRUE)

qplot(msa_summary$ots_pct_refin, geom="histogram") +theme_minimal()+xlab("Fraction of OTS Loans 2008-2009 (Refinance)")+ggtitle("")
```


```{r eval=FALSE,include=FALSE}
# Propensity to deny using the fraction of OTS loans in each census tract
rm(regs)
gc(verbose = FALSE)
regs <- list()
regs[[1]] <- felm(as.formula("denied~ots_pct_refin*factor(asofdate)+ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|censustract+asofdate+applicantrace1|0|censustract"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate>2007 & hmda$msa_loans_2009>30])


note =c("Fixed Effects:  Census tract ,Year, Race","Standard Errors clustered by Census tract","Sample restricted to census tracts with more than 30 loans, period after 2008")
# denied~log(ots_pct_refin)*post+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa+asofdate+applicantrace1|0|msa
# denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa+asofdate

printtable(regs,c(""),"I(denied)",note,"none","")
```



```{r}
# msa_summary_purch <- hmda[hmda$actiontaken %in% c(1,3) & hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate %in% c("2008","2009"), .(count = .N), by = list(msa,ots_lender)]
# msa_summary_purch <- dcast(msa_summary_purch,formula =msa~ots_lender )
# names(msa_summary_purch) <- c("msa","nonots_purch","ots_purch")
# # msa_summary_purch$nonots_purch <- ifelse(is.na(msa_summary_purch$nonots_purch),0,msa_summary_purch$nonots_purch)
# # msa_summary_purch$ots_purch <- ifelse(is.na(msa_summary_purch$ots_purch),0,msa_summary_purch$ots_purch)
# msa_summary_purch <- data.table(msa_summary_purch)
# 
# msa_summary_purch[,ots_pct_purch:=msa_summary_purch$ots_purch/(msa_summary_purch$ots_purch+msa_summary_purch$nonots_purch)]

msa_summary_refin <- hmda[hmda$actiontaken %in% c(1,2,3) & hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate==2009, .(count = .N), by = list(msa,ots_lender)]
msa_summary_refin <- dcast(msa_summary_refin,formula =msa~ots_lender )
names(msa_summary_refin) <- c("msa","nonots_refin","ots_refin")
# msa_summary_refin$nonots_refin <- ifelse(is.na(msa_summary_refin$nonots_refin),0,msa_summary_refin$nonots_refin)
# msa_summary_refin$ots_refin <- ifelse(is.na(msa_summary_refin$ots_refin),0,msa_summary_refin$ots_refin)
msa_summary_refin <- data.table(msa_summary_refin)
msa_summary_refin[,ots_pct_refin:=msa_summary_refin$ots_refin/(msa_summary_refin$ots_refin+msa_summary_refin$nonots_refin)]

msa_summary <- msa_summary_refin#merge(msa_summary_purch,msa_summary_refin,by="msa")

msa_summary[,msa_loans_2009:=msa_summary$nonots_refin+msa_summary$ots_refin]
msa_summary[,c("nonots_purch","ots_purch","nonots_refin","ots_refin"):=list(NULL)]

# msa_summary[,ots_pct_purch_q:= ntile(msa_summary$ots_pct_purch,4)]
# msa_summary[,ots_pct_refin_q:= ntile(msa_summary$ots_pct_refin,4)]

```

```{r read_freddie_data}
rm(hmda)
rm(reg)
rm(regs)
gc()
loan_month <- readRDS(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/processed data/freddie per data/freddie_data_loan_month.rds")


loan_month[,default:=ifelse(loan_month$CURRENTLOANDELINQ>=1,1,0)]
loan_month[,foreclosed:= ifelse(loan_month$ZEROBALANCECODE>=3 & !is.na(loan_month$ZEROBALANCECODE),1,0)]
loan_month[,prepaid:=ifelse(loan_month$ZEROBALANCECODE==1 & !is.na(loan_month$ZEROBALANCECODE),1,0)]



```
# Zillow Data
```{r}
# zillow_rent <- readRDS(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/creditsupplyshock.rds")
#   zillow_rent[,c("zip3_big4_frac","big4_nbig4","msa","city","msa_big4_frac","rent_1","zip")] <- list(NULL)
#   names(zillow_rent)[1] = "MSA"
  
zillow_rent <- read.csv(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/Affordability_ChainedZRI_2018Q3.csv")
zillow_rent$RegionID <- NULL
zillow_rent$SizeRank <- NULL

zillow_rent <- melt(zillow_rent,id.vars = c("RegionName"))
zillow_rent['year'] <- substr(zillow_rent$variable,2,5)
zillow_rent['month'] <- substr(zillow_rent$variable,7,8)
zillow_rent <- zillow_rent[zillow_rent$month=="12",]
zillow_rent$variable <- NULL
zillow_rent$month <- NULL
zillow_rent$RegionName <- as.character(zillow_rent$RegionName)

names(zillow_rent) <- c("msa","rent","year")
zillow_rent['city'] <- tolower(zillow_rent$msa)

library(zipcode)
data("zipcode")
zipcode$city <- tolower(paste(zipcode$city,", ",zipcode$state,sep=""))
zipcode[,c("state","latitude","longitude")] <- list(NULL)

zillow_rent <- merge(zillow_rent,zipcode,by="city",all.x = TRUE)

unmatched <- read.csv(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/unmatched_msa_2.csv")
unmatched$msa <- as.character(unmatched$msa)
zillow_rent <- merge(zillow_rent,unmatched,by="msa",all.x = TRUE)
zillow_rent$zip <- ifelse(is.na(zillow_rent$zip),zillow_rent$zip2,zillow_rent$zip)
zillow_rent <- zillow_rent[!is.na(zillow_rent$zip),]
zillow_rent <- zillow_rent[!is.na(zillow_rent$rent),]
zillow_rent$zip2 <- NULL
zillow_rent$zip <- as.integer(zillow_rent$zip)

zip_cbsa <- read.csv(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/ZIP_CBSA_092018.csv")
zillow_rent <- merge(zillow_rent,zip_cbsa,by="zip",all.x = TRUE)
not_na <- unique(zillow_rent[!is.na(zillow_rent$cbsa),]$msa)
yes_na <- unique(zillow_rent[is.na(zillow_rent$cbsa),]$msa)
unmatched <- not_na[!not_na %in% yes_na]
zillow_rent <- zillow_rent[!is.na(zillow_rent$cbsa),]
zillow_rent <- zillow_rent[!duplicated(zillow_rent[,c("cbsa","year")]),]

zillow_rent <- zillow_rent[!is.na(zillow_rent$rent),]
zillow_rent$msa <- NULL
zillow_rent$year <- as.numeric(zillow_rent$year)
zillow_rent$zip <- NULL
zillow_rent$city <- NULL

names(zillow_rent) <- c("rent","year","MSA")



loan_month <- merge(loan_month,zillow_rent,by=c("MSA","year"))

# loan_month <- loan_month[loan_month$log_delta_rent >-0.2 & loan_month$log_delta_rent<0.2]
# loan_month <- loan_month[loan_month$current_equity>-1]

cols.to.del <- c("REPURCHASEFLAG","MODIFICATIONFLAG","MODIFICATIONCOST","FIRSTPAYMENTDATE","MATURITYDATE","NUMBEROFUNITS","LOANTERM","org_hpi","current_hpi","POSTALCODE")
loan_month[,(cols.to.del):=NULL]

# loan_month <- loan_month[loan_month$log_delta_rent >-0.1 & loan_month$log_delta_rent<0.1]
# loan_month <- loan_month[!is.na(loan_month$credit_supply_shock_1)]
loan_month[,default_2:=ifelse(!loan_month$CURRENTLOANDELINQ %in% c("0","1","2","3","4"),1,0)]
loan_month[,default:=ifelse(!loan_month$CURRENTLOANDELINQ %in% c("0"),1,0)]


loan_month <- merge(loan_month,msa_summary,by.x=c("MSA"),by.y = "msa")
loan_month[,post := ifelse(loan_month$CURRENTMONTH>="2011-06-01",1,0)]
```

# ACS Data
```{r}
# library(tidycensus)
# census_api_key("06b232797e7854aad802d7c7d8673c337fe1b29a")
# 
# for(year in 2017:2010) {
#           print(year)
#           temp <- get_acs(geography = "metropolitan statistical area/micropolitan statistical area", year = year,output = "wide",
#                          variables = c("B19013_001E","B01002_001E","B01003_001E","B02001_003E","B02001_002E","B07013_003E","B10058_002E","B06009_004E"))
#           temp['year'] <- year
#           temp[,c("B19013_001M","B01002_001M","B01003_001M","B02001_003M","B02001_002M","B07013_003M","B10058_002M","B06009_004M")] <- NULL
#           write.table(temp,file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_msa_2.csv",col.names = FALSE,row.names = FALSE,sep="|",quote = FALSE,append = TRUE)
# }
# temp$year = 2009
# write.table(temp,file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_msa_2.csv",col.names = FALSE,row.names = FALSE,sep="|",quote = FALSE,append = TRUE)
# temp$year = 2008
# write.table(temp,file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_msa_2.csv",col.names = FALSE,row.names = FALSE,sep="|",quote = FALSE,append = TRUE)

acs_data <- fread("C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_msa_2.csv",sep="|",stringsAsFactors = FALSE,header = FALSE)
names(acs_data) <- c("MSA","name","medianhhincome","medianage","totalpopulation","blackpopulation","whitepopulation","renters","laborforce","collegedegree","year")
acs_data$name <- NULL
acs_data[,white_frac:= acs_data$whitepopulation/acs_data$totalpopulation]
acs_data[,renter_frac:= acs_data$renters/acs_data$totalpopulation]
acs_data[,collegedegree_frac:= acs_data$collegedegree/acs_data$totalpopulation]
acs_data[,c("blackpopulation","whitepopulation","renters","laborforce","collegedegree"):=list(NULL)]

loan_month[,c("name","medianhhincome","medianage","totalpopulation","blackpopulation","whitepopulation","renters","laborforce","collegedegree"):=list(NULL)]

loan_month <- merge(loan_month,acs_data,by=c("MSA","year"),all.x=TRUE)

```


# BLS Data
```{r}
bls_data <- fread(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/bls_unemp_metro.txt")
bls_data[,MSA:=as.integer(substr(bls_data$series_id,8,12))]
bls_data[,month:=as.Date(paste(bls_data$year,substr(bls_data$period,2,3),"01",sep="-"))]
bls_data[,series:=substr(bls_data$series_id,19,20)]
bls_data <- bls_data[bls_data$series=="03"]
bls_data[,c("series_id","year","period","footnote_codes","series"):=list(NULL)]
names(bls_data) <- c("unemp_rate","MSA","month")
bls_data <- bls_data[!duplicated(bls_data[,c("MSA","month")])]
bls_data <- bls_data[bls_data$month >= "2008-01-01"]
setkey(bls_data,MSA,month)

setkey(loan_month,MSA,month)
loan_month <- merge(loan_month,bls_data,by=c("MSA","month"),all.x=TRUE)


```


# Default on otc_fraction x after2011

```{r}

note =c("Fixed Effects: Loan, Year, MSA","Standard Errors clustered by Loan")

# controls = "LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)+unemp_rate+log(medianhhincome)+log(totalpopulation)+white_frac+renter_frac+collegedegree_frac|factor(year)+factor(MSA)+factor(LOANNO)"
controls = "LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)+unemp_rate+log(medianhhincome)+log(totalpopulation)+white_frac+renter_frac+collegedegree_frac|factor(year)+factor(MSA)+factor(LOANNO)"

formulas <- list()

# formulas[[1]] <- as.formula(paste("default~log(rent)|factor(year)+factor(MSA)+factor(LOANNO)+factor(SELLERNAME)|0|LOANNO",sep=""))
formulas[[1]] <- as.formula(paste("default~ots_pct_refin*post|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))
formulas[[2]] <- as.formula(paste("default~ots_pct_refin*post+",controls,"|0|LOANNO+MSA",sep=""))

# formulas[[3]] <- as.formula(paste("default~1|factor(year)+factor(MSA)+factor(LOANNO)+factor(SELLERNAME)|(log(rent)~credit_supply_shock_1)|LOANNO",sep=""))


rm(iv_reg)
iv_reg <- list()
iv_reg[[1]] <- felm(formulas[[1]], data=loan_month)
# iv_reg[[1]]$residuals <- NULL
# iv_reg[[1]]$c.fitted.values <- NULL
# iv_reg[[1]]$fitted.values <- NULL
# iv_reg[[1]]$r.residuals <- NULL
# iv_reg[[1]]$response <- NULL
# iv_reg[[1]]$robustvcv <- NULL
# iv_reg[[1]]$inv <- NULL
# iv_reg[[1]]$fe <- NULL
gc()
iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
gc()
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
# iv_reg[[3]] <- felm(formulas[[3]], data=loan_month) #[loan_month$CURRENTLOANDELINQ<=1,]
# 
# 
# condf <- c("Cond. F. Stat","","",round(condfstat(iv_reg[[3]])[[1]],2))

printtable(iv_reg,c("OLS","First Stage","IV"),"default",note,"credit supply shock",list("condf"))
```



#  Default on otc_fraction x after2011: parellel trends
```{r}
rm(iv_reg)
gc()
# loan_month[,year:= as.integer(loan_month$year)]
loan_month[,year:= as.factor(loan_month$year)]
loan_month <- within(loan_month, year <- relevel(year, ref = 4))
formulas[[3]] <- as.formula(paste("default~ots_pct_refin*factor(year)|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))


iv_reg <- list()

iv_reg[[1]] <- felm(formulas[[3]], data=loan_month)
gc()
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
# iv_reg[[3]] <- felm(formulas[[3]], data=loan_month) #[loan_month$CURRENTLOANDELINQ<=1,]
# 
# 
# condf <- c("Cond. F. Stat","","",round(condfstat(iv_reg[[3]])[[1]],2))

# sample <- within(sample, year <- relevel(year, ref = 6))
printtable(iv_reg,c("OLS","First Stage","IV"),"default","","credit supply shock",list("condf"))
```


```{r}
coefs <- c(as.vector(iv_reg[[1]]$coefficients[11:13]),0,as.vector(iv_reg[[1]]$coefficients[14:19]))
se <- c(as.vector(iv_reg[[1]]$cse[11:13]),0,as.vector(iv_reg[[1]]$cse[14:19]))
se_lb <- coefs - se*1.96
se_ub <- coefs + se*1.96
years <- c(2008:2017)

df <- as.data.frame(cbind(years,coefs),stringsAsFactors = FALSE)

gr1<- ggplot(df, aes(x=years, y=coefs)) + geom_hline(yintercept = 0)+
  geom_point(color="red")+geom_errorbar(aes(ymin=se_lb, ymax=se_ub), width=0,position=position_dodge(0))+
  scale_x_continuous(breaks=years)+ theme_bw()+ylab(expression(beta[y])) + xlab("")+
  theme(legend.title=element_blank(),panel.border = element_blank(), axis.line.x = element_line(color = 'gray80'))
gr1
```


# Default on otc_fraction x after2011: Binned Scatter Plot
```{r}
adj_default <- felm(default~1|factor(year)+factor(MSA)+factor(LOANNO),data=loan_month[!is.na(loan_month$ots_pct_refin) & loan_month$post==1])
adj_default_resid <- adj_default$residuals

adj_ots_shock <- felm(ots_pct_refin~1|factor(year)+factor(MSA)+factor(LOANNO),data=loan_month[loan_month$post==1])
adj_ots_shock_resid <- adj_ots_shock$residuals

resids <- as.data.frame(cbind(adj_ots_shock_resid,adj_default_resid))
names(resids) <- c("ots_frac","adj_default_resid")

resids <- resids[resids$ots_frac>=quantile(resids$ots_frac,0.01)  & resids$ots_frac<=quantile(resids$ots_frac,0.99),]


# resids['ots_frac_rounded'] <- floor(resids$ots_frac*1e32)/1e32
resids['ots_frac_percent'] <- ntile(resids$ots_frac,100)

resids <- data.table(resids)

resids_summary <- resids[,list(mean_default=mean(adj_default_resid)),by=list(ots_frac_percent)]
resids_summary[,group:="post"]

adj_default <- felm(default~1|factor(year)+factor(MSA)+factor(LOANNO),data=loan_month[!is.na(loan_month$ots_pct_refin) & loan_month$post==0 ])
adj_default_resid <- adj_default$residuals

adj_ots_shock <- felm(ots_pct_refin~1|factor(year)+factor(MSA)+factor(LOANNO),data=loan_month[loan_month$post==0 ])
adj_ots_shock_resid <- adj_ots_shock$residuals


resids2 <- as.data.frame(cbind(adj_ots_shock_resid,adj_default_resid))
names(resids2) <- c("ots_frac","adj_default_resid")

resids2 <- resids2[resids2$ots_frac>=quantile(resids2$ots_frac,0.01)  & resids2$ots_frac<=quantile(resids2$ots_frac,0.99),]


# resids['ots_frac_rounded'] <- floor(resids$ots_frac*1e32)/1e32
resids2['ots_frac_percent'] <- ntile(resids2$ots_frac,100)

resids2 <- data.table(resids2)

resids2_summary <- resids2[,list(mean_default=mean(adj_default_resid)),by=list(ots_frac_percent)]
resids2_summary[,group:="pre"]

resid_sum <- rbind(resids_summary,resids2_summary)
# 
# g1 = ggplot(resid_sum,aes(x=ots_frac_percent,y=mean_default,color=group))+geom_point(aes(group=group))+geom_smooth(method="lm",formula=y~x,se=FALSE,color="red")+xlab("Percentile of FE adjusted OTS Fraction")+ylab("FE adjusted default")+theme_minimal()+theme(legend.position="bottom",legend.title = element_blank())
# g1

g2 = ggplot(resid_sum[resid_sum$mean_default<=0.005 & resid_sum$mean_default>= (-0.005)]
            ,aes(x=ots_frac_percent,y=mean_default,color=group,shape=group))+geom_point(size=3)+geom_smooth(method=lm, formula =  y ~ x,se=FALSE, fullrange=TRUE)+xlab("Percentile of FE adjusted OTS Fraction")+ylab("FE adjusted default")+theme_minimal()+theme(legend.position="bottom",legend.title = element_blank())
g2


```

#  Default on otc_fraction x after2011: FICO Split

```{r}

# loan_month[,fico_qs:=ntile(loan_month$CREDITSCORE,4)]
rm(iv_reg)
gc()
iv_reg <- list()

iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$CREDITSCORE<=700])
iv_reg[[2]] <- felm(formulas[[2]], data=loan_month[loan_month$CREDITSCORE> 700 & loan_month$CREDITSCORE<=750])
iv_reg[[3]] <- felm(formulas[[2]], data=loan_month[loan_month$CREDITSCORE> 750 & loan_month$CREDITSCORE<=780])
iv_reg[[4]] <- felm(formulas[[2]], data=loan_month[loan_month$CREDITSCORE>780])

printtable(iv_reg,c("<700","700-750","750-780",">780"),"default",note,"credit supply shock","")


```



#  Default on otc_fraction x after2011: CLTV Split

```{r}

iv_reg <- list()
iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$CLTV<=80])
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month[loan_month$CLTV==80])
iv_reg[[2]] <- felm(formulas[[2]], data=loan_month[loan_month$CLTV> 80])


printtable(iv_reg,c("<=80",">80"),"default",note,"","")

```

# Default on otc_fraction x after2011: Loan Amount Split
```{r}
rm(iv_reg)
gc()
iv_reg <- list()
iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$ORIGINALUPB<=125000])
iv_reg[[2]] <- felm(formulas[[2]], data=loan_month[loan_month$ORIGINALUPB> 125000 & loan_month$ORIGINALUPB<=250000])
iv_reg[[3]] <- felm(formulas[[2]], data=loan_month[loan_month$ORIGINALUPB>250000])

printtable(iv_reg,c("<125k","125k-250k",">250k"),"default",note,"","")


```


# Default on otc_fraction x after2011: DTI split
```{r}
rm(iv_reg)


iv_reg <- list()
iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$DTI<=30])
iv_reg[[2]] <- felm(formulas[[2]], data=loan_month[loan_month$DTI> 30 & loan_month$DTI<=40])
iv_reg[[3]] <- felm(formulas[[2]], data=loan_month[loan_month$DTI>40])

printtable(iv_reg,c("<=30","30-40",">40"),"default",note,"","")


```
