---
title: "OTS -> OCC"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
```

```{r}
rm(list=ls())
library(data.table)
library(lfe)
library(stargazer)
library(plyr)
library(reshape2)
library(lubridate)
library(ggplot2)
library(reshape2)
library(dplyr)

hmda <- readRDS(file="C:/Users/dnratnadiwakara/Documents/interest rate and default/Data/Raw/HMDA/agency_hmda.rds")


#variables
output.type="text"


# functions
printtable <- function(reg,column.labels,depvar,note,iv,lines) {
  stargazer(reg,type=output.type,no.space = TRUE,omit.stat = c("f","adj.rsq","ser"),notes= note,column.labels = column.labels, dep.var.labels = "",dep.var.caption   = paste("Y: ",gsub("_"," ",depvar),"; iv: ",gsub("_"," ",iv)),dep.var.labels.include = FALSE,add.lines = lines)
}


fes <- readRDS(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/big4_propensity_to_deny.rds")

zillow_rent <- readRDS(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/creditsupplyshock.rds")
  zillow_rent[,c("zip3_big4_frac","big4_nbig4","msa","city","msa_big4_frac","rent_1","zip")] <- list(NULL)
  names(zillow_rent)[1] = "MSA"
  
  ffiec<- readRDS(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/FFIEC.rds")
  zillow_rent <- merge(zillow_rent,ffiec,by=c("MSA","year"),all.x = TRUE)
  
  zillow_rent_p_1 <- zillow_rent[,c("MSA","year","rent")]
  zillow_rent_p_1$year <- zillow_rent_p_1$year-1
  names(zillow_rent_p_1) <- c("MSA","year","rent_p_1")
  
  zillow_rent <- merge(zillow_rent,zillow_rent_p_1,by=c("MSA","year"),all.x = TRUE)
  
  zillow_rent_cs <- zillow_rent[,c("MSA","year","credit_supply_shock","log_delta_rent")]
  zillow_rent_cs$year <- zillow_rent_cs$year+1
  names(zillow_rent_cs) <- c("MSA","year","credit_supply_shock_1","log_delta_rent_1")
  
  zillow_rent <- merge(zillow_rent,zillow_rent_cs,by=c("MSA","year"),all.x = TRUE)
  rm(zillow_rent_cs)
  rm(zillow_rent_p_1)
```


# Descriptives: Owneroccupied, new purchase
```{r}
stargazer(hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1", c("denied","amountofloan","loan_to_income","fha","asofdate")], type = "text", summary.stat = c("mean","median","sd", "n"),notes = "",digits = 4)
```
# Descriptives: Owneroccupied, refinance
```{r}
stargazer(hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3", c("denied","amountofloan","loan_to_income","fha","asofdate")], type = "text", summary.stat = c("mean","median","sd", "n"),notes = "",digits = 4)
```



```{r eval=FALSE,include=FALSE}
# Propensity to deny: complete sample
gc()
regs <- list()
regs[[1]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" ])
gc()
regs[[2]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" ])

note =c("Fixed Effects:  MSA*Year, MSA*OTS, Race","Standard Errors clustered by MSA")


printtable(regs,c("New purchases","Refinances"),"denied",note,"none","")
rm(regs)
gc()
```

# Propensity to deny: loan applications after 2008
```{r }

gc()
regs <- list()
regs[[1]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate>=2008])
gc()
regs[[2]] <- felm(as.formula("denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3"  & hmda$asofdate>=2008])

note =c("Fixed Effects:  MSA*Year, MSA*OTS, Race","Standard Errors clustered by MSA")


printtable(regs,c("New purchases","Refinances"),"denied",note,"none","")
rm(regs)
gc(verbose = FALSE)
```

# Propensity to deny: parellel trends
```{r }
rm(regs)
gc()
regs <- list()
regs[[1]] <- felm(as.formula("denied~factor(asofdate)*factor(ots_lender)+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" ])
gc()
regs[[2]] <- felm(as.formula("denied~factor(asofdate)*factor(ots_lender)+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" ])

note =c("Fixed Effects:  MSA*Year, MSA*OTS, Race","Standard Errors clustered by MSA,Year")


printtable(regs,c("New purchases","Refinances"),"denied",note,"none","")
```


 
# Fraction of OTS loans in census tracts in 2008-2009
```{r}
msa_summary_purch <- hmda[hmda$actiontaken %in% c(1,3) & hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate %in% c("2008","2009"), .(count = .N), by = list(censustract,ots_lender)]
msa_summary_purch <- dcast(msa_summary_purch,formula =censustract~ots_lender )
names(msa_summary_purch) <- c("censustract","nonots_purch","ots_purch")
# msa_summary_purch$nonots_purch <- ifelse(is.na(msa_summary_purch$nonots_purch),0,msa_summary_purch$nonots_purch)
# msa_summary_purch$ots_purch <- ifelse(is.na(msa_summary_purch$ots_purch),0,msa_summary_purch$ots_purch)
msa_summary_purch <- data.table(msa_summary_purch)

msa_summary_purch[,ots_pct_purch:=msa_summary_purch$ots_purch/(msa_summary_purch$ots_purch+msa_summary_purch$nonots_purch)]

msa_summary_refin <- hmda[hmda$actiontaken %in% c(1,2,3) & hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate==2009, .(count = .N), by = list(censustract,ots_lender)]
msa_summary_refin <- dcast(msa_summary_refin,formula =censustract~ots_lender )
names(msa_summary_refin) <- c("censustract","nonots_refin","ots_refin")
# msa_summary_refin$nonots_refin <- ifelse(is.na(msa_summary_refin$nonots_refin),0,msa_summary_refin$nonots_refin)
# msa_summary_refin$ots_refin <- ifelse(is.na(msa_summary_refin$ots_refin),0,msa_summary_refin$ots_refin)
msa_summary_refin <- data.table(msa_summary_refin)
msa_summary_refin[,ots_pct_refin:=msa_summary_refin$ots_refin/(msa_summary_refin$ots_refin+msa_summary_refin$nonots_refin)]

msa_summary <- merge(msa_summary_purch,msa_summary_refin,by="censustract")

msa_summary[,msa_loans_2009:=msa_summary$nonots_purch+msa_summary$ots_purch+msa_summary$nonots_refin+msa_summary$ots_refin]
msa_summary[,c("nonots_purch","ots_purch","nonots_refin","ots_refin"):=list(NULL)]

msa_summary[,ots_pct_purch_q:= ntile(msa_summary$ots_pct_purch,4)]
msa_summary[,ots_pct_refin_q:= ntile(msa_summary$ots_pct_refin,4)]

hmda[,c("ots_pct_purch","ots_pct_refin","msa_loans_2009","ots_pct_purch_q","ots_pct_refin_q"):=list(NULL)]
hmda<- merge(hmda,msa_summary,by="censustract",all.x = TRUE)
hist(msa_summary$ots_pct_purch,main = "OTS Loan Fraction 2008-2009: New purchases")
hist(msa_summary$ots_pct_refin,main="OTS Loan Fraction 2008-2009: Repurchases")
plot(msa_summary$ots_pct_purch,msa_summary$ots_pct_refin)
```



# Propensity to deny using the fraction of OTS loans in each census tract
```{r}

rm(regs)
gc(verbose = FALSE)
regs <- list()
regs[[1]] <- felm(as.formula("denied~ots_pct_purch*post+ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|censustract+asofdate+applicantrace1|0|censustract"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate>2007 & hmda$msa_loans_2009>30])
gc()
regs[[2]] <- felm(as.formula("denied~ots_pct_refin*post+ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|censustract+asofdate+applicantrace1|0|censustract"),data =hmda[hmda$actiontaken %in% c(1,3) &  hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate>2007 & hmda$msa_loans_2009>30])


note =c("Fixed Effects:  Census tract ,Year, Race","Standard Errors clustered by Census tract","Sample restricted to census tracts with more than 30 loans, period after 2008")
# denied~log(ots_pct_refin)*post+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa+asofdate+applicantrace1|0|msa
# denied~post*ots_lender+fha+log(applicantincome)+log(amountofloan)+loan_to_income|msa_time+ots_msa+applicantrace1|0|msa+asofdate

printtable(regs,c("Purchases","Refinances"),"I(denied)",note,"none","")
```



```{r}
msa_summary_purch <- hmda[hmda$actiontaken %in% c(1,3) & hmda$occupancy=="1" & hmda$purposeofloan=="1" & hmda$asofdate %in% c("2008","2009"), .(count = .N), by = list(msa,ots_lender)]
msa_summary_purch <- dcast(msa_summary_purch,formula =msa~ots_lender )
names(msa_summary_purch) <- c("msa","nonots_purch","ots_purch")
# msa_summary_purch$nonots_purch <- ifelse(is.na(msa_summary_purch$nonots_purch),0,msa_summary_purch$nonots_purch)
# msa_summary_purch$ots_purch <- ifelse(is.na(msa_summary_purch$ots_purch),0,msa_summary_purch$ots_purch)
msa_summary_purch <- data.table(msa_summary_purch)

msa_summary_purch[,ots_pct_purch:=msa_summary_purch$ots_purch/(msa_summary_purch$ots_purch+msa_summary_purch$nonots_purch)]

msa_summary_refin <- hmda[hmda$actiontaken %in% c(1,2,3) & hmda$occupancy=="1" & hmda$purposeofloan=="3" & hmda$asofdate==2009, .(count = .N), by = list(msa,ots_lender)]
msa_summary_refin <- dcast(msa_summary_refin,formula =msa~ots_lender )
names(msa_summary_refin) <- c("msa","nonots_refin","ots_refin")
# msa_summary_refin$nonots_refin <- ifelse(is.na(msa_summary_refin$nonots_refin),0,msa_summary_refin$nonots_refin)
# msa_summary_refin$ots_refin <- ifelse(is.na(msa_summary_refin$ots_refin),0,msa_summary_refin$ots_refin)
msa_summary_refin <- data.table(msa_summary_refin)
msa_summary_refin[,ots_pct_refin:=msa_summary_refin$ots_refin/(msa_summary_refin$ots_refin+msa_summary_refin$nonots_refin)]

msa_summary <- merge(msa_summary_purch,msa_summary_refin,by="msa")

msa_summary[,msa_loans_2009:=msa_summary$nonots_purch+msa_summary$ots_purch+msa_summary$nonots_refin+msa_summary$ots_refin]
msa_summary[,c("nonots_purch","ots_purch","nonots_refin","ots_refin"):=list(NULL)]

msa_summary[,ots_pct_purch_q:= ntile(msa_summary$ots_pct_purch,4)]
msa_summary[,ots_pct_refin_q:= ntile(msa_summary$ots_pct_refin,4)]

```




```{r}
rm(hmda)
rm(regs)
gc()
# these files were created by 03 create_loan_month_freddie.R
file_list<- list.files(path="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/processed data/freddie per data",pattern="*.rds",full.names = TRUE)
loan_month = lapply(file_list, function (x) data.table(readRDS(x)))
loan_month = rbindlist(loan_month, fill = TRUE)
loan_month[ ,zip3:= loan_month$POSTALCODE]
loan_month[ ,month:= loan_month$CURRENTMONTH]
loan_month[ ,year := as.numeric(substr(loan_month$month,1,4))]

loan_month[,default:=ifelse(loan_month$CURRENTLOANDELINQ>=1,1,0)]
loan_month[,foreclosed:= ifelse(loan_month$ZEROBALANCECODE>=3 & !is.na(loan_month$ZEROBALANCECODE),1,0)]
loan_month[,prepaid:=ifelse(loan_month$ZEROBALANCECODE==1 & !is.na(loan_month$ZEROBALANCECODE),1,0)]

loan_month <- merge(loan_month,msa_summary,by.x=c("MSA"),by.y = "msa")


cols.to.del <- c("REPURCHASEFLAG","MODIFICATIONFLAG","MODIFICATIONCOST","FIRSTPAYMENTDATE","MATURITYDATE","NUMBEROFUNITS","LOANTERM","org_hpi","current_hpi","POSTALCODE")
loan_month[,(cols.to.del):=NULL]

loan_month[,post := ifelse(loan_month$CURRENTMONTH>="2011-06-01",1,0)]

# loan_month <- merge(loan_month,temp,by=c("MSA","year"),all.x=TRUE)


# saveRDS(loan_month,file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/freddie_loanmonth_cleaned_merged_with_rentt.rds")

```





# Propensity to deny

```{r}

note =c("Fixed Effects: Loan, Year, MSA","Standard Errors clustered by Loan")


formulas <- list()

# formulas[[1]] <- as.formula(paste("default~log(rent)|factor(year)+factor(MSA)+factor(LOANNO)+factor(SELLERNAME)|0|LOANNO",sep=""))

formulas[[1]] <- as.formula(paste("default~ots_pct_refin*post+LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))
formulas[[2]] <- as.formula(paste("default~ots_pct_refin*factor(year)+LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))

# formulas[[3]] <- as.formula(paste("default~1|factor(year)+factor(MSA)+factor(LOANNO)+factor(SELLERNAME)|(log(rent)~credit_supply_shock_1)|LOANNO",sep=""))


rm(iv_reg)
iv_reg <- list()
iv_reg[[1]] <- felm(formulas[[1]], data=loan_month)
gc()
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
# iv_reg[[3]] <- felm(formulas[[3]], data=loan_month) #[loan_month$CURRENTLOANDELINQ<=1,]
# 
# 
# condf <- c("Cond. F. Stat","","",round(condfstat(iv_reg[[3]])[[1]],2))

printtable(iv_reg,c("OLS","First Stage","IV"),"default",note,"credit supply shock",list("condf"))
```



# Propensity to deny: parellel trends
```{r}
rm(iv_reg)
iv_reg <- list()
gc()
iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$year %in% 2008:2014])
gc()
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
# iv_reg[[3]] <- felm(formulas[[3]], data=loan_month) #[loan_month$CURRENTLOANDELINQ<=1,]
# 
# 
# condf <- c("Cond. F. Stat","","",round(condfstat(iv_reg[[3]])[[1]],2))

printtable(iv_reg,c("OLS","First Stage","IV"),"default",note,"credit supply shock",list("condf"))
```


```{r}

# # https://api.census.gov/data/2012/acs5/variables.html
# # https://www.census.gov/data/developers/data-sets/acs-5year.2016.html
# 
# library(RJSONIO)
# variables <- c("B19013_001E","B01002_001E","B01003_001E")#,"B07413_003E")#,"B27011_014E")
# names <- c("MedianHouseholdIncome","MedianAge","TotalPopulation")#,"Renters")#,"Unemployed")
# years <- 2010:2017
# 
# 
# 
# for(i in 1:length(variables)) {
#   print(i)
#   for(year in years) {
#     if(year<=2009) {
#                 baseurl = paste("https://api.census.gov/data/",year,"/acs5?for=metropolitan%20statistical%20area/micropolitan%20statistical%20area&get=",sep="")
#     }
#     if(year>2009) {
#           baseurl = paste("https://api.census.gov/data/",year,"/acs/acs5?for=metropolitan%20statistical%20area/micropolitan%20statistical%20area:*&get=",sep="")
#     }
# 
# 
# 
#     fullurl = paste(baseurl,variables[i],sep="")
# 
#     temp <- fromJSON(fullurl)
# 
#     fullurl = paste(baseurl,variables[i],sep="")
# 
#     temp <- fromJSON(fullurl)
# 
#     temp<- as.data.frame(do.call("rbind", temp))
# 
#     # temp <- apply(temp,2,as.character)
#     # temp <- as.data.frame(temp)
#     # temp[,1] <- as.character(temp[,1])
#     # temp[,2] <- as.character(temp[,2])
#     #
#     temp <- temp[2:nrow(temp),]
#     temp['year'] <- year
#     temp['variable'] <- names[i]
#     temp[,1] <- as.character(temp[,1])
#     temp[,2] <- as.character(temp[,2])
#     write.table(temp,file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_Jan2019.csv",col.names = FALSE,row.names = FALSE,sep="|",quote = FALSE,append = TRUE)
#   }
# }

temp <- read.csv(file="C:/Users/dnratnadiwakara/Documents/rent_strategic_default/acs_Jan2019.csv",sep="|",stringsAsFactors = FALSE,header = FALSE)
names(temp) <- c("value","MSA","year","variable")

temp <- dcast(temp,formula=MSA+year~variable)
temp <- data.table(temp)

loan_month[,c("MedianAge","MedianHouseholdIncome","TotalPopulation"):=list(NULL)]
loan_month <- merge(loan_month,temp,by=c("MSA","year"),all.x=TRUE)
```



# Propensity to deny: parellel trends with demographic controls
```{r}
note =c("Fixed Effects: Loan, Year, MSA","Standard Errors clustered by Loan, MSA")


formulas <- list()

# formulas[[1]] <- as.formula(paste("default~log(rent)|factor(year)+factor(MSA)+factor(LOANNO)+factor(SELLERNAME)|0|LOANNO",sep=""))

formulas[[1]] <- as.formula(paste("default~ots_pct_refin*post+LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))
formulas[[2]] <- as.formula(paste("default~ots_pct_refin*factor(year)+LOANAGE+I(LOANAGE^2)+I(LOANAGE^3)+current_equity*log(current_housevalue)+MedianAge+log(MedianHouseholdIncome)+log(TotalPopulation)|factor(year)+factor(MSA)+factor(LOANNO)|0|LOANNO+MSA",sep=""))



rm(iv_reg)
iv_reg <- list()
gc()
iv_reg[[1]] <- felm(formulas[[2]], data=loan_month[loan_month$year %in% 2008:2014])
gc()
# iv_reg[[2]] <- felm(formulas[[2]], data=loan_month)
# iv_reg[[3]] <- felm(formulas[[3]], data=loan_month) #[loan_month$CURRENTLOANDELINQ<=1,]
# 
# 
# condf <- c("Cond. F. Stat","","",round(condfstat(iv_reg[[3]])[[1]],2))

printtable(iv_reg,c("OLS","First Stage","IV"),"default",note,"credit supply shock",list("condf"))
```
